Highly Available Transactions: Virtues and Limitations

### 2013-03-20 writeup/evaluation.tex
more writing
More writing

\section{evaluation}

V. Evaluation (1.5pg)

The goal in this section is twofold:
1.) Look at existing algorithms and their coordination cost in the abstract
2.) Perform limited real-world deployments to validate these abstract costs

@@

@@

>>>>

\section{Analysis}
\label{sec:evaluation}

With a firm understanding of which of several ACID and distributed
consistency properties are available and not, we perform analysis of
their implications for existing algorithms, applications, and
deployments. Specifically:

\begin{enumerate}
\item We revisit traditional database concurrency control with a focus
  on coordination costs and on high availability.
\item We examine the properties required by a realistic OLTP
  application patterned on TPC-C.
\item We perform a brief experimental evaluation of HAT versus non-HAT
  properties on public cloud infrastructure.
\end{enumerate}

\subsection{Existing Algorithms}

As we have discussed, many existing database transaction and
concurrency control algorithms are not designed for high
availability. These algorithms often presume a single-server
deployment or the requirement for serializability. As a consequence,
traditional transaction processing systems are not well-optimized for
a HAT context.

 designed for either single-node deployments or
to achieve the are designed for

@@

\subsection{Application Requirements}

@@

\subsection{Experimental Costs}

### 2013-03-20 writeup/hat-vldb.tex
checkpoint writing
more writing
More writing

\documentclass{vldb}
\usepackage{times, graphicx, url, xcolor, multicol, minipage, subfig}
\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)

@@

\begin{abstract}
foo bar baz
\end{abstract}

@@

\subsection{References}

Generated by bibtex from your ~.bib file. Run latex, then bibtex, then
latex twice (to resolve references).

>>>>

\documentclass{vldb}
\usepackage{times, graphicx, url, xcolor, multicol, minipage, subfig, tikz}
\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)

\usetikzlibrary{positioning, snakes, shapes}

@@

\begin{abstract}
Given the presence of network latency and the possibility of partial
failure and network partitions, many systems eschew transactional
functionality providing strong semantic guarantees on groups of
multiple operations over multiple data items. In this work, we
consider the problem of providing transactional guarantees that are
highly available, or do not suffer from network latency or system
partitions.  We introduce a new taxonomy of highly available
algorithms and analyze a combination of ACID and distributed
consistency guarantees to identify which can and cannot be achieved by
Highly Available Transaction (HAT) systems. In doing so, we
analytically and experimentally quantify the cost of violating high
availability as well as the cost of providing necessarily relaxed
semantics.
\end{abstract}

@@
